---
title: "run-nested-GLMNET-ml4calibrated450k"
author: "mematt"
date: "4/27/2019"
output: 
  html_notebook: 
    toc: yes
    toc_depth: 4
---

# ml4calibrated450k - Elastic Net penalized Multinomial Logistic Regression (ELNET) using the `glmnet`package

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r}
# 1. Source utility/subfunctions (low level)
source("subfunctions_GLMNET.R")
# Installs and loads the required packages doMC, glmnet, c060

# 2. Source train function (mid level)
source("train_GLMNET.R")

# 3. Source nestedcv function (high level)
source("nestedcv_GLMNET.R")
```

***

## Run

### Define parallel backend using `doMC` 

```{r}
# Register parallel backend --------------------------------------------------------------------------------------------------------------------

# 1. doMC  ----------------------------------------------------------------------------------------------------------------------
library(doMC)
# <Note> that you can register a different parallel backend later, or deregister doMC by registering the sequential backend by calling the `registerDoSEQ()` function

# Detect cores(/threads)
n_threads <- cores <- detectCores()-1 # leave 1 thread for the OS
registerDoMC(cores)
#registerDoMC(cores = n_threads)
# Check backend
getDoParVersion()    # "1.3.5"
getDoParWorkers()    # 
getDoParRegistered() # TRUE
#registerDoSEQ()


# Test parallel backend if it is running/functioning - by Hadley Wickham - AdvR p.374. ---------------------------------------------
my_pause <- function(i){
  function(x) Sys.sleep(i)
}

system.time(lapply(1:10, my_pause(0.25)))
#   user  system elapsed 
#  0.008   0.000   2.502
system.time(mclapply(1:10, my_pause(0.25), mc.cores = cores)) # 64
#   user  system elapsed 
#  0.004   0.272   0.269
```

***

### Load `y.RData` and `nfolds.RData` objects into the global environment (.GlobalEnv) 

These are going to be fetched automatically from `.GlobalEnv` by the `run_nestedcv_GLMNET()` function

```{r}
# Load needed data objects ---------------------------------------------------------------------------------------------------------------------

# Local path if "./data" folder is in the working directory
load("./data/y.RData")
load("./data/nfolds.RData")

# Suggested path in `rocker` (docker) container for R 
# load("/home/rstudio/data/y.RData")
# load("/home/rstudio/data/nfolds.RData")
```

***

### Function call `run_nestedcv_GLMNET()` with concurrent tuning of the `alpha` and `lambda` hyperparameters

Default >> `y.. = NULL`, `betas.. = NULL` reading `betas.K.k.RData` objects from folder path `"... /data/betas.train.test.10k.filtered/"`

See also **Figure 1., steps 7 - 10 | Internal validation**.

```{r}
# Run time: alpha = {0; 0.025; 0.05; 0.075; 0.1} with nCV = 5x on i9 7960x CPU @ 32 threads:
# => for 10k => 2h - 2h 15 min /(sub)fold => 1.0 - 5.5 ~72h  
# => for  1k => 12-15 min /(sub)fold => 1.0 - 5.5 ~7.5h 

Sys.time()
run_nestedcv_GLMNET(y.. = NULL,
                    betas.. = NULL,
                    path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/",
                    fname.betas.p.varfilt = "betas",
                    subset.CpGs.1k = T, # subset to 1k # "fast track"
                    n.cv.folds = 5, 
                    nfolds.. = NULL,
                    K.start = 1, k.start = 0, 
                    K.stop = NULL, k.stop = NULL,
                    n.cv.folds.cvglmnet = 5,
                    alpha.min. = 0, alpha.max. = 0.1, by. = 0.025,  # focus on ridge & ridge-like settings
                    cores = n_threads, 
                    seed. = 1234, 
                    out.path = "GLMNET-1k",  
                    out.fname = "CVfold")
Sys.time()
```



