---
title: "calibrate-vRF-tRF-ml4calibrated450k"
author: "mematt"
date: "5/12/2019"
output: 
  word_document: 
    toc: yes
    toc_depth: 4
---

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r, echo=TRUE, tidy=TRUE}
# 1. Source subfunctions for Platt scaling (LR)
source("calibration_Platt_LR.R")

# 2. Source subfunctions for Platt scaling (FLR)
source("calibration_Platt_FLR.R")

# 3. Source subfunctions for multinomial ridge regression (MR)
source("calibration_MR.R")

# 4. Source the integrated wrapper of all (LR, FLR, MR) the above
source("calibrator_integrated_wrapper_LR_FLR_MR.R")
```

**<NOTE>** to speed up performance parallel backend can be registered. See the `README.md` of the GitHub repository or the other scripts.

***

### Figure 1. steps 11 - 13  | Calibration 

#### Example code to calibrate vRF 

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
calibrate_LR(out.path = "vRF-calibrated-LR/",
             out.fname = "probsCVfold",
             nfolds.. = NULL,
             y.. = NULL,
             load.path.w.name = "./vRF/CVfold.",
             which.optimized.metric.or.algorithm = "vanilla", 
             save.metric.name.into.output.file = T,
             verbose.messages = F)


calibrate_FLR(out.path = "vRF-calibrated-FLR/",
              out.fname = "probsCVfold",
              nfolds.. = NULL,
              y.. = NULL,
              load.path.w.name = "./vRF/CVfold.",
              which.optimized.metric.or.algorithm = "vanilla",
              save.metric.name.into.output.file = T,
              verbose.messages = T)



calibrate_MR(out.path = "/vRF-calibrated-MR/",
             out.fname = "probsCVfold",
             nfolds.. = NULL,
             y.. = NULL,
             load.path.w.name = "./vRF/CVfold.",
             verbose.messages = T,
             which.optimized.metric.or.algorithm = "vanilla", 
             save.metric.name.into.output.file = T,
             parallel.cv.glmnet = T,
             setseed = 1234)

```


***

#### Example code chunk to calibrate using all algorithms (LR, FLR, MR) on each tRF metric separately

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
# tRF_BS + {LR; FLR; MR} ----------------------------------------------------------------------------------------------------
Sys.time()
t_calib_integrated_all_tRF_BS <- system.time(
  calibrator_integrated_wrapper(out.path = "./tRF-BS-calibrator-integrated/",
                                load.path.w.name = "./tRF/CVfold.",
                                which.optimized.metric.or.algorithm = "brier",
                                which.calibrator = "all",
                                verbose.messages = F,
                                save.metric.name.into.output.file = T,
                                parallel.cv.glmnet = T,
                                setseed = 1234)

)
Sys.time()

# # tRF_ME + {LR; FLR; MR} ----------------------------------------------------------------------------------------------------
Sys.time()
t_calib_integrated_all_tRF_ME <- system.time(
  calibrator_integrated_wrapper(out.path = "./tRF-ME-calibrator-integrated/",
                                load.path.w.name = "./tRF/CVfold.",
                                which.optimized.metric.or.algorithm = "miscerr",
                                which.calibrator = "all",
                                verbose.messages = F,
                                save.metric.name.into.output.file = T,
                                parallel.cv.glmnet = T,
                                setseed = 1234)

)
Sys.time()

# # tRF_LL + {LR; FLR; MR} ----------------------------------------------------------------------------------------------------
Sys.time()
t_calib_integrated_all_tRF_LL <- system.time(
  calibrator_integrated_wrapper(out.path = "./tRF-LL-calibrator-integrated/",
                                load.path.w.name = "./tRF/CVfold.",
                                which.optimized.metric.or.algorithm = "mlogl",
                                which.calibrator = "all",
                                verbose.messages = F,
                                save.metric.name.into.output.file = T,
                                parallel.cv.glmnet = T,
                                setseed = 1234)

)
Sys.time()
```

***

#### Code chunck to perform calibration with all algorithms (LR, FLR, MR) on all evaluation metrics of tRF (BS, ME, LL) concurrently

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
### Run all for each metric and all calibration algorithms -------------------------------------------------------------------------------------------------------------------------------------------------------
tRF.opt.metrics.folder.name <- c("BS", "ME", "LL")
tRF.folder.path <- as.list(rep(paste("tRF",
                                     tRF.opt.metrics.folder.name, 
                                     "calibrator-integrated", 
                                     sep = "-"), 
                               each = 3))
tRF.opt.metrics.long.RData <- rep(c("brier", "miscerr", "mlogl"), each = 3)
calibrator.name <- c("LR", "FLR", "MR")
tRF.fname.stump <- as.list(paste("probsCVfold",
                                 tRF.opt.metrics.long.RData,
                                 rep(calibrator.name, 3),
                                 sep = ".")
                           )

# Short call using mapply
tRF.l.perfevals.all <- mapply(FUN = performance_evaluator, 
                              load.path.folder = tRF.folder.path, 
                              load.fname.stump = tRF.fname.stump)
tRF.l.perfevals.all # matrix

# Add colnames
colnames(tRF.l.perfevals.all) <- tRF.fname.stump
# Rename
tRF_ALL_LR_FLR_MR_perfeval <- try.l.perfevals.all

# Save
#save(tRF_ALL_LR_FLR_MR_perfeval, file = "./performance evaluation/tRF_ALL_LR_FLR_MR_perfeval.RData")
```

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
tRF.l.perfevals.all
```

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
tRF_ALL_LR_FLR_MR_perfeval[, 1:3]
```
```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
tRF_ALL_LR_FLR_MR_perfeval[, 4:6]
```

```{r, eval=FALSE, echo=TRUE, tidy=TRUE}
tRF_ALL_LR_FLR_MR_perfeval[, 7:9]
```

