---
title: "run-nested-tRF-ml4calibrated450k"
author: "mematt"
date: "4/20/2019"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
---

# ml4calibrated450k - tuned RF (tRF)

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r}
# 1. Source utility/subfunctions (low level)
# the required evaluation metrics (BS, ME, LL, AUC) needed for `p` variable selection tuning are also sourced here
# required libraries are loaded or installed if needed
source("subfunctions_tunedRF.R")

# 2. Source train function (mid level)
source("train_tunedRF.R")

# 3. Source nestedcv function (high level)
source("nestedcv_tunedRF.R")
```

***

## Run

### Define parallel backend using `doMC` 

```{r}
# Register parallel backend ---------------------------------------------------------------------------------------------------------------------------------------

# 1. doMC  ----------------------------------------------------------------------------------------------------------------------
library(doMC)
# <Note> that you can register a different parallel backend later, or deregister doMC by registering the sequential backend by calling the `registerDoSEQ()` function

# Detect cores(/threads)
n_threads <- cores <- detectCores()-1 # leave 1 thread for the OS
#cores <- 16         # AWS64 - caret 16 * rfp(4)
registerDoMC(cores)
#registerDoMC(cores = n_threads)
# Check backend
getDoParVersion()    # "1.3.5"
getDoParWorkers()    # 
getDoParRegistered() # TRUE
#registerDoSEQ()


# Test parallel backend if it is running/functioning - by Hadley Wickham - AdvR p.374. ---------------------------------------------
my_pause <- function(i){
  function(x) Sys.sleep(i)
}

system.time(lapply(1:10, my_pause(0.25)))
#   user  system elapsed 
#  0.008   0.000   2.502
system.time(mclapply(1:10, my_pause(0.25), mc.cores = cores)) # 64
#   user  system elapsed 
#  0.004   0.272   0.269
```

***

### Load `y.RData` and `nfolds.RData` objects into the global environment (.GlobalEnv) 

These are going to be fetched automatically from `.GlobalEnv` by the `run_nestedcv_tunedRF()` function

```{r}
# Load needed data objects --------------------------------------------------------------------------------------------------------------------

# Local path if "./data" folder is in the working directory
load("./data/y.RData")
load("./data/nfolds.RData")

# Suggested path in `rocker` (docker) container for R 
# load("/home/rstudio/data/y.RData")
# load("/home/rstudio/data/nfolds.RData")
```

***

### Function call `run_nestedcv_tunedRF()` 

#### Default >> `y.. = NULL`, `betas.. = NULL` reading `betas.K.k.RData` objects from folder path `"... /data/betas.train.test.10k.filtered/"`

See also **Figure 1., steps 7 - 10 | Internal validation**.

```{r}
# Run the function that performs the task

Sys.time() # ~ 21 mins / pro fold  | nCV=5 @ 72 threads AWS c5n.18xlarge

run_nestedcv_tunedRF(y.. = NULL, 
                     betas.. = NULL, 
                     path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/",
                     fname.betas.p.varfilt = "betas",
                     subset.CpGs.1k = F, 
                     n.cv.folds = 5, 
                     nfolds..= NULL,    
                     K.start = 1, k.start = 0,
                     K.stop = NULL, k.stop = NULL,
                     n.cv = 5, n.rep = 1, 
                     mtry.min = 80, mtry.max = 110, length.mtry = 4, 
                     ntrees.min = 500, ntrees.max = 2000, ntree.by = 500,
                     use.default.nodesize.1.only = T, 
                     nodesize.proc = c(0.01, 0.05, 0.1),
                     p.n.pred.var = c(100, 200, 500, 1000, 2000, 5000, 7500, 10000),
                     cores = cores, 
                     seed = 1234,
                     out.path = "tRF", 
                     out.fname = "CVfold")
Sys.time()
 
# registerDoSEQ() # switch back to sequential (single core) # if using doMC backend 
```


#### Fast track: test run on 1k data

Limited settings on 1000 CpGs with 3x-fold extra nested CV for RF hyperparameter tuning (n.cv = 3)

```{r}
Sys.time() # ~ 2-3 min / pro fold @ 11 threads rMBP i9
run_nestedcv_tunedRF(y.. = NULL, 
                     betas.. = NULL, 
                     path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/",
                     fname.betas.p.varfilt = "betas",
                     subset.CpGs.1k = T, 
                     n.cv.folds = 5, 
                     nfolds.. = NULL,   
                     K.start = 1, k.start = 1,
                     K.stop = 1, k.stop = 2,
                     n.cv = 3, n.rep = 1, 
                     mtry.min = 30, mtry.max = 40, length.mtry = 2, 
                     ntrees.min = 200, ntrees.max = 400, ntree.by = 200,
                     use.default.nodesize.1.only = T, 
                     nodesize.proc = c(0.01, 0.05, 0.1),
                     p.n.pred.var = c(100, 200, 500, 1000),
                     cores = cores, 
                     seed = 1234,
                     out.path = "tRF-test-run-1k", 
                     out.fname = "CVfold")
Sys.time()
```

***
