---
title: "run-nested-SVM-LiblineaR-ml4calibrated450k"
author: "mematt"
date: "4/27/2019"
output: 
  html_notebook: 
    toc: yes
    toc_depth: 4
---

# ml4calibrated450k - Support Vector Machines (SVM) with linear kernels (LK) using the `LiblineaR`package

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r}
# 1. Source utility/subfunctions (low level)
source("subfunctions_SVM_LiblineaR.R")
# Installs and loads the required packages doMC, LiblineaR, e1071

# 2. Source train function (mid level)
source("train_SVM_LiblineaR.R")

# 3. Source nestedcv function (high level)
source("nestedcv_SVM_LiblineaR.R")
```

***

## Run

### Define parallel backend using `doMC` 

```{r}
# Register parallel backend --------------------------------------------------------------------------------------------------------------------

# 1. doMC  ----------------------------------------------------------------------------------------------------------------------
library(doMC)
# <Note> that you can register a different parallel backend later, or deregister doMC by registering the sequential backend by calling the `registerDoSEQ()` function

# Detect cores(/threads)
n_threads <- cores <- detectCores()-1 # leave 1 thread for the OS
registerDoMC(cores)
#registerDoMC(cores = n_threads)
# Check backend
getDoParVersion()    # "1.3.5"
getDoParWorkers()    # 
getDoParRegistered() # TRUE
#registerDoSEQ()


# Test parallel backend if it is running/functioning - by Hadley Wickham - AdvR p.374. ---------------------------------------------
my_pause <- function(i){
  function(x) Sys.sleep(i)
}

system.time(lapply(1:10, my_pause(0.25)))
#   user  system elapsed 
#  0.008   0.000   2.502
system.time(mclapply(1:10, my_pause(0.25), mc.cores = cores)) # 64
#   user  system elapsed 
#  0.004   0.272   0.269
```

***

### Load `y.RData` and `nfolds.RData` objects into the global environment (.GlobalEnv) 

These are going to be fetched automatically from `.GlobalEnv` by the `run_nestedcv_SVM_LiblineaR()` function

```{r}
# Load needed data objects ---------------------------------------------------------------------------------------------------------------------

# Local path if "./data" folder is in the working directory
load("./data/y.RData")
load("./data/nfolds.RData")

# Suggested path in `rocker` (docker) container for R 
# load("/home/rstudio/data/y.RData")
# load("/home/rstudio/data/nfolds.RData")
```

***

### Function call `run_nestedcv_SVM_LiblineaR()` with hyperparameter (C, cost) tuning 

Default >> `y.. = NULL`, `betas.. = NULL` reading `betas.K.k.RData` objects from folder path `"... /data/betas.train.test.10k.filtered/"`

See also **Figure 1., steps 7 - 10 | Internal validation**.

The `run_nestedcv_SVM_LiblineaR()` function performs hyperparameter (C, cost) tuning using 5-fold extra nested CV within the training loop for  
1. type 0: L2-regularized logistic regression (L2LR) and  
2. type 4: Crammer & Singer SVC models

```{r}
# <INFO>
# L2-LR:
# Run time: ~ 100 min/fold with nCV = 5 for C = {0.001, 0.01} @ 11 threads @ i7 6850k 
# Run time: ~ 9h 45min/fold with nCV=5 for C=10⁻3:3 @ i9 7960x @ 32 cores for L2-LR! (especially for C>10)
# Crammer Singer type 4 SVC:
# Run time: ~ 13-15 min/fold with nCV=5 for C=10⁻3:3 @ i7 7700k @ 8 cores => ~6h for full (5x5) run.

# <CRITICAL> when running only the type 4 – support vector classification by Crammer and Singer ==> 
#           set `mod.type = 4` and `type4.CramSing = F` ; otherwise CS-SVC runs 2x.

# Fitting type 4 CS-SVC only -------------------------------------------------------------------------------------------------------------------
Sys.time() # [1] "2019-04-30 13:28:27 UTC"
run_nestedcv_SVM_LiblineaR(y.. = NULL, 
                           betas.. = NULL, 
                           path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/",
                           fname.betas.p.varfilt = "betas",
                           subset.CpGs.1k = F, 
                           n.cv.folds = 5, 
                           nfolds.. = NULL,   
                           K.start = 1, k.start = 0,
                           K.stop = NULL, k.stop = NULL, 
                           n.CV. = 5,  # extra nested tuning within the training loop
                           C.base = 10, C.min = -3, C.max = 3, 
                           mod.type = 4, 
                           type4.CramSing = F, # only class estimates no probability estimates
                           parallel = T,
                           n.mc.cores = n_threads,
                           seed = 1234, 
                           out.path = "SVM-LiblineaR-10k-nCV-5x-type4-CS", 
                           out.fname = "CVfold")
Sys.time() # [1] "2019-04-30 19:23:40 UTC"
```
