---
title: "run-nested-SVM-e1071-ml4calibrated450k"
author: "mematt"
date: "4/27/2019"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
---

# ml4calibrated450k - Support Vector Machines (SVM) linear kernels (LK) using `e1071` package

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r}
# 1. Source utility/subfunctions (low level)
# required libraries are loaded or installed if needed
source("subfunctions_SVM_e1071.R")

# 2. Source train function (mid level)
source("train_SVM_e1071.R")

# 3. Source nestedcv function (high level)
source("nestedcv_SVM_e1071.R")
```

***

## Run

### Define parallel backend using `doMC` 

```{r}
# Register parallel backend ---------------------------------------------------------------------------------------------------------------------------------------

# 1. doMC  ----------------------------------------------------------------------------------------------------------------------
library(doMC)
# <Note> that you can register a different parallel backend later, or deregister doMC by registering the sequential backend by calling the `registerDoSEQ()` function

# Detect cores(/threads)
n_threads <- cores <- detectCores()-1 # leave 1 thread for the OS
#cores <- 16         # AWS64 - caret 16 * rfp(4)
registerDoMC(cores)
#registerDoMC(cores = n_threads)
# Check backend
getDoParVersion()    # "1.3.5"
getDoParWorkers()    # 
getDoParRegistered() # TRUE
#registerDoSEQ()


# Test parallel backend if it is running/functioning - by Hadley Wickham - AdvR p.374. ---------------------------------------------
my_pause <- function(i){
  function(x) Sys.sleep(i)
}

system.time(lapply(1:10, my_pause(0.25)))
#   user  system elapsed 
#  0.008   0.000   2.502
system.time(mclapply(1:10, my_pause(0.25), mc.cores = cores)) # 64
#   user  system elapsed 
#  0.004   0.272   0.269
```

***

### Load `y.RData` and `nfolds.RData` objects into the global environment (.GlobalEnv) 

These are going to be fetched automatically from `.GlobalEnv` by the `run_nestedcv_tunedRF()` function

```{r}
# Load needed data objects ---------------------------------------------------------------------------------------------------------------------------------------

# Local path if "./data" folder is in the working directory
load("./data/y.RData")
load("./data/nfolds.RData")

# Suggested path in `rocker` (docker) container for R 
# load("/home/rstudio/data/y.RData")
# load("/home/rstudio/data/nfolds.RData")
```

***

### Function call `run_nestedcv_SVM_e1071()` 

#### Default >> `y.. = NULL`, `betas.. = NULL` reading `betas.K.k.RData` objects from folder path `"... /data/betas.train.test.10k.filtered/"`

See also **Figure 1., steps 7 - 10 | Internal validation**.

```{r}
# Run time:  ~ 50-70 min / (sub)fold  @ 11 threads @ Intel Core i7 6850k 
Sys.time() 
run_nestedcv_SVM_e1071(y.. = NULL, 
                       betas.. = NULL, 
                       path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/",
                       fname.betas.p.varfilt = "betas",
                       subset.CpGs.1k = F, 
                       n.cv.folds = 5, 
                       nfolds.. = NULL,
                       K.start = 1, k.start = 0,
                       K.stop = NULL, k.stop = NULL, 
                       n.CV. = 5,  # extra nested tuning in training loop
                       C.base = 10, C.min = -3, C.max = 1,
                       n.mc.cores = n_threads,   
                       seed = 1234, 
                       out.path = "SVM-e1071-10k", 
                       out.fname = "CVfold")
Sys.time()
```

