---
title: "run-nested-vRF-ml4calibrated450k"
author: "mematt"
date: "4/18/2019"
output: 
  html_document: 
    toc: yes
    toc_depth: 4
---

# ml4calibrated450k - vanilla RF (vRF)

## Source dependencies: libraries, scripts and functions

Please make sure that the sourced scripts are in the same folder.

```{r}
# 1. Source utility/subfunctions (low level)
source("subfunctions_vRF")

# 2. Source train function (mid level)
source("train_vRF.R")

# 3. Source nestedcv function (high level)
source("nestedcv_vRF.R")

# 4. optional - for performance evaluation
# the required evaluation metrics (BS, ME, LL, AUC) needed for performance evaluation
source("evaluation_metrics.R")
```

***

## Run

### Define parallel backend using `doMC` 

```{r}
# Register parallel backend ---------------------------------------------------------------------------------------------------------------------------------------

# 1. doMC  ----------------------------------------------------------------------------------------------------------------------
library(doMC)

# Detect cores(/threads)
n_threads <- cores <- detectCores()-2 # leave 2 threads for OS
# Note that you can register a different parallel backend later, or deregister doMC by registering the sequential backend by calling the `registerDoSEQ()` function
registerDoMC(cores)
#registerDoMC(cores = n_threads)
getDoParVersion()    # "1.3.5"
getDoParWorkers()    # 
getDoParRegistered() # TRUE
#registerDoSEQ()     # switch back to sequential (single core) # if using doMC backend 


# Test parallel backend if it is running/functioning - by Hadley Wickham - AdvR p.374. -------------------------------------------
my_pause <- function(i){
  function(x) Sys.sleep(i)
}

system.time(lapply(1:10, my_pause(0.25)))
#   user  system elapsed 
#  0.008   0.000   2.502
system.time(mclapply(1:10, my_pause(0.25), mc.cores = cores)) # 10
#   user  system elapsed 
#  0.004   0.272   0.269
```

***

### Load `y.RData` and `nfolds.RData` objects into the global environment (.GlobalEnv) 

These are going to be fetched automatically from `.GlobalEnv` by the `run_nestedcv_vRF()` function

```{r}
# Load needed data objects ---------------------------------------------------------------------------------------------------------------------------------------

# Local path if "./data" folder is in the working directory
load("./data/y.RData")
load("./data/nfolds.RData")

# Suggested path in `rocker` (docker) container for R 
# load("/home/rstudio/data/y.RData")
# load("/home/rstudio/data/nfolds.RData")
```

***

### Function call `run_nestedcv_vRF()` with default settings $ntrees = 500, p = 200, mtry = sqrt(10000)$

#### Default >> `y.. = NULL`, `betas.. = NULL` reading `betas.K.k.RData` objects from folder path `"... /data/betas.train.test.10k.filtered/"`

See also **Figure 1., steps 7 - 10 | Internal validation**.

```{r}
# Run the function that performs the task - with default settings

# RUN TIME: overall ~38 mins ;  ~ 1 min - 1 min 45s / (sub)fold  | nCV = 5 @ 10 threads i9 rMBP 15" (2018)
Sys.time()
run_nestedcv_vRF(path.betas.var.filtered = "/home/rstudio/data/betas.train.test.10k.filtered/", 
                 fname.betas.p.varfilt = "betas",
                 subset.CpGs.1k = F, 
                 cores = n_threads)
Sys.time()
```

